Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-31 sections/results.tex
fix some sentence joiners

Figure \ref{fig:scatter} shows the relationship between usefulness class from our classification model and comment sets from manual assessment. 
The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} classification model. The comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless. While, the comments drawn in the white area are those not satisfied any condition (i.e. \emph{undetermined}). 
The total number of comments from this classification results is described in Table \ref{tb:classify_number}.

>>>>

Figure \ref{fig:scatter} shows the relationship between usefulness class from our classification model and comment sets from manual assessment. 
The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} classification model. The comments drawn in the green area are those satisfied condition of useful model, and the comments drawn in the red area are those satisfied condition of useless, while the comments drawn in the white area are those not satisfied any condition (i.e. \emph{undetermined}). 
The total number of comments from this classification results is described in Table \ref{tb:classify_number}.
